% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
% (c) 2011 Callie Vandeweile <calliev@gmail.com> http://web.cecs.pdx.edu/~calliev
% (c) 2011 Spencer Krum <me@spencerkrum.com> http://www.nibalizer.com
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.75in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\LARGE \href{www.nibalizer.com}{Spencer Krum}} & \href{mailto:me@spencerkrum.com}{me@spencerkrum.com}\\
	{\footnotesize \texttt{709 SW 16th Ave \#110, Portland OR 97205}} & \textcolor{mygreylink}{{619.980.7820}} \\
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader
    \item Worked as a part of the Unix/Linux team administering servers and services: NFS, Puppet, Samba, iSCSI, KVM/libvirt, LVM, ZFS, DHCP/PXE, DNS,  LDAP, Apache, Linux, FreeBSD, Solaris, Out-of-band management interfaces, VNC, vlan tagging, Amanda Network Backup, serial interfaces, IRC server administration, 
    \item Developed team-based skills and experience: IRC, git, tickets, self-documentation on wiki 
    \item Gained the skill of 1 Problem 2 Write a little utility in bash/python 3 Done


%%%%%%%%%%%%%%%%%%%%%%
\resheading{\href{http://www.derekhildreth.com/portfolio.php}{Skills}}
	\begin{description}
		\item[Management, Organization, Leadership:] {\footnotesize  3+ years experience managing paid staff \& volunteers in a variety of settings including student leadership and community partnership development. Self motivated and driven with excellent time management skills.  Flexible, able to learn new skills quickly and adapt to evolving workplace scenarios.}
        \item[Communication:] { \footnotesize Fluent in Spanish.  Practical experience with research and interviewing, gained on the job bilingually in Central America. Solid background in conflict management. Extensive experience professionally writing in a variety fields and formats, including fund development, public relations, journalism, and emerging social medias.}

	\end{description} % End Skills list


%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{description}
		\item
			\ressubheading{Portland State University}{Portland, OR}{\href{http://www.pdx.edu/hatfieldschool/division-public-administratio}{Masters in Public Administration (in progress)} \textcolor{mygreylink}{}}{Jun. 2010 -- Present}
		\item
			\ressubheading{Pacific University}{Forest Grove, OR}{\href{http://www.pacificu.edu/as/politics}{Bachelor of Arts in Politics \& Government}; \textcolor{mygreylink}{magna cum laude}}{Aug. 2006 -- May. 2008}
		\item
			\ressubheading{Clackamas Community College}{Oregon City, OR}{\href{http://www.clackamas.edu/index.aspx}{AAOT General Studies}; \textcolor{mygreylink}{summa cum lauda}}{Jun. 2003 -- Jun. 2006}
	\end{description} % End Education list






%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
	\begin{description}
		\item 
			\ressubheading{Girl Scouts of Oregon and SW Washington}{Portland, OR}{\textcolor{mygreylink}{Program Coordinator}}{Jun. 2010 -- Present}
				{ \footnotesize
				\begin{itemize}
                \resitem{Coordinates \& Manages the Highest Award Program for the Portland Metro Area, Eastern Oregon, Salem area, North Coast in Oregon and Skamania \& Clark counties in Washington}
                \resitem{Supervises 20+ volunteers on GSOSW Travel and Award Teams in Portland and Salem areas.}
                \resitem{Develops and maintains connections with organizations throughout Oregon and SW Washington that provide Girl Scout programming.}
                \resitem{Provides direct trainings, workshops and programming for girls ages 11-18 as well as adult Girl Scout volunteers.}
                \resitem{Manages combined travel, award and event budget for service areas.}
				\end{itemize}
				}
		\item


			\ressubheading{Presbyterian Church USA}{Coban, Alta Verapaz, Guatemala}{\textcolor{mygreylink}{Young Adult Volunteer}}{Aug. 2008 -- Aug. 2009}
				{ \footnotesize
				\begin{itemize}
                    \resitem{Conducted anthropological research surveying Q’eqchi’ communities in the outlying Alta Verapaz region.}
                    \resitem{Assisted visiting groups with Food for the Hungry and CEDEPCA as a translator.}
                    \resitem{Provided support for workshops providing women’s rights education throughout rural Guatemala with CEDEPCA.}
				\end{itemize}
          			}
		\item			
			\ressubheading{Pacific University Center for Gender Equity}{Forest Grove, OR}{\textcolor{mygreylink}{Student Co-Director}}{Aug. 2007 -- May 2008}
				{ \footnotesize				
				\begin{itemize}
                    \resitem{Directed and managed a student staff of 12 in organizing on campus events, speakers \& educational campaigns.}
                    \resitem{Fostered the development of an internal mentorship program designed to develop leadership skills of incoming freshman and sophomore staff.}
                    \resitem{Managed a budget of approximately \$10,000}
                    \resitem{Promoted after one year as a student  programmer in 2006/07.}
				\end{itemize}
				}

	\end{description} % End Education list
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Volunteer Activities}
	\begin{description}
		\item			
			\ressubheading{Computer Action Team}{Portland, OR}{\textcolor{mygreylink}{Desk Operations Group}}{Oct. 2010 -- Present}
				{ \footnotesize				
				\begin{itemize}
                    \resitem{MCECS Computer Action Team, Portland State University, Portland OR}
                    \resitem{IT Tech support volunteer, responsible for IT troubleshooting, customer-service and support.}
				\end{itemize}
				}

	\end{description} % End Education list


\end{document}


%%%%%%%%%%%%%%%%%%%%%%
% Would have completed this if I had not had all projects listed under "Skills".  
% Still a good idea.  See if I can fit it in somewhere...  Otherwise, just print it out and bring it to an interview if needed.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{Hardware Engineering Projects} % If printed as a seperate page, get more detailed in the descriptions!  What type of processor?  What program used? Etc.
	
	\begin{description}
		\item[4 and 8 bit RISC CPUs] {\footnotesize Simple CPUs designed using CircuitMaker (no HDL) which contained ALUs, counters, registers, and 1K RAM all designed from scratch}
		\item[Simple Calculator] {\footnotesize Designed a simple calculator from the ground up using Xilinx ISE and Verilog HDL} % Get schematic block diagram for this one!
		\item[Stereo Amplifier] {\footnotesize Contained I/O as well as bass, treble, and volume controls}
		\item[Power Supply Basics] {\footnotesize Learned about the very basics of power supply design using transformers, rectifiers, and zener diodes and voltage regulators.} 
		\item[Parallel Port Game Controller] {\footnotesize Went through the start to finish development process of a game controller including driver development, microprocessor  \& ADC design (8255 MicroBoard; N.I.	ADC0809), and PCB design}
		\item[Portable Microphone Amplifier] {\footnotesize Utilized a series of transistors to amplify sound in a room with a potentiometer as volume control}
		\item[MP3 Player] {\footnotesize Developed an MP3 player using the Analog Devices BlackFin BF533 microprocessor and EZ-KIT development kit which utilized interrupts and audio codec}  % get link to block diagram for this one!
		\item[INL Remote Cell Phone Control] {\footnotesize Senior project which developed a prototype for Idaho National Laboratories allowing them to remote control a cell phone via 802.11g and bluetooth at a range greater than 6000ft consisting of 3 major components: central control, wireless medium, and embedded systems for chuckar box}
		\item[Inverted Pendulum] {\footnotesize Used sliding mode feedback control and inverted pendulum kit to keep metal rod standing vertially on a swingin arm}
		\item[FM Transmitter] {\footnotesize Built a simple FM Transmitter based off of given schematics as an introduction to FM modulation signals}
	\end{description}


\resheading{Software Engineering Projects}  % There really are a TON of projects I can put on this, but here are some major ones:
	\begin{description}
		\item[Book Keyword Scanner] {\footnotesize Developed a program which will take any input file and, given a keyword search, will return the frequency of that word }
		\item[Pedigree Chart] {\footnotesize Developed a program which will parse through a pedigree file and display a pedigree chart in the command line}
		\item[Factory Nail Rejection] {\footnotesize This program was simulating a factory which produced nails that had to be a very specific length, and if it wasn't, the program would reject it}
		\item[Calendar Program] {\footnotesize Given the time and date to display, the calendar program would display a simple calendar on the command line which took into account leap years}
		\item[Normal Distribution] {\footnotesize This program simulated the classic wheel of fortune blinko game where several thousand chip were statistially recorded and displayed as they dropped into a board filled with pegs}
		\item[RSA Encryption] {\footnotesize Developed an application which utilized the RSA encryption method to encrypt and decrypt messages}
	\end{description}

\end{document}

%Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{References}
	\begin{center}
		\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
			Toby Rummans & Eric Karl & Gordon Smith \\
			Entry Level Web Developer & Computer Science \& Engineering  & Technology Support Specialist \\ 
			\vspace{10pt} 
			Memolinkcorp & BYU-Idaho & BYU-Idaho \\ 
			[removed] & 525 South Center St. & 525 South Center St.  \\
			Denver, CO 80210 & Rexburg ID 83460 & Rexburg ID 83460 \\
			[removed] & (208) 496-3097 & (208) 496-2816 \\
		\end{tabular*}
	\end{center}
	
% \end{document}


% ADDITIONAL WORK EXPERIENCE NOT INCLUDED	OR OLD

		\item 
			\ressubheading{\href{http://www.rexburgmotorsports.com/}{Rexburg Motorsports}}{Rexburg, ID}{Computer Systems Administrator}{Aug. 2006 -- Oct. 2006}
				{ \footnotesize
				\begin{itemize}
	            			\resitem{Managed file and application servers running Windows 2003 Server}
	            			\resitem{Performed all levels of hardware and software systems support for 40 computers and 10 printers}
				\end{itemize}
				}

		\item 
			\ressubheading{Bresnan Communications}{Billings, MT}{Teir 1 Technical Support}{Jan. 2006 -- April 2006}
				{ \footnotesize
				\begin{itemize}
					\resitem{Provided Bresnan customers with technical support over the phone.}
					\resitem{Receieved training on resolving networking, cable TV, and VOIP issues.}
				\end{itemize}
				}

		\item 
			\ressubheading{Northwestern Energy}{Billings, MT}{Summer Gas/Electrical Engineer}{May 2004 -- April 2005}
				\begin{itemize}
					\resitem{Interned with full time Gas/Electrical Engineers.}
					\resitem{Documented, mapped, and marked city streetlights using MS Access, GTViewer, FRAMME, and CAD.}
				\end{itemize} 


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge. 
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
reporting information, editing, interviewing, and facilitating group discussion. 
 
- Research and Planning: The ability to search for specific knowledge and formulate a 
program for a definite course of action. Skills like forecasting, predicting, identifying 
issues, finding alternatives, gathering information, solving problems, setting goals, 
extracting information, and developing strategies. 
 
- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
people, and help people. Skills like providing support for others, listening, delegating 
with respect, representing others, asserting, developing rapport, and perceiving 
feelings. 
 
- Management, Organization, Leadership: The ability to supervise others and guide 
individuals and groups towards the completion of tasks. Skills like managing groups, 
selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
enlisting help. 

Source: 
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources: 
http://www.tvmier.com/Resume_Education.html

