% Spencer O. Krum - Curriculum Vitae
% 
%
% Copyright (C) 2012 Spencer Krum
% 
% Template (C) 2004-2010 - Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Fonts
\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}
\usepackage[scaled=0.85]{beramono}

% Set your name here
\def\name{Spencer O. Krum}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {Open Soruce, Puppet, Netflix, Intern, Chemistry, Computer Science, Programming,
    Undergraduate, Physics},
  pdftitle = {\name: Spencer Krum Resume},
  pdfsubject = {Spencer Krum},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  Spencer Krum\\
  708 Sw 16th Ave \#110\\
  Portland, OR 97205
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Mobile: (619) 980-7820 \\
  Email: \texttt{krum.spencer@gmail.com} \\
  Homepage: \texttt{http://github.com/nibalizer} \\
\end{minipage}

\section*{Objective}

When AWS went down, Netflix stayed up. I want to work with you guys.
\\

\begin{minipage}[t]{0.5\textwidth}
\section*{Core Skills}
\begin{itemize}
\item Verbal communication, Enthusiasm, \& Energy
\item Linux/Unix-fu
\item Puppet-fu, Python-fu, shell-fu
\item Sysadmin/Puppet hands on production experience
\end{itemize}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\section*{Education}
\begin{itemize}

  \item B.S., Physics
  \item Portland State University, Portland, OR
  \item Emphasis on Computer Science
  \item Expected graduation: Fall 2013
  
\end{itemize}
\end{minipage}

\renewenvironment{itemize}{
  \begin{list}{$\bullet$}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}
\section*{Relevant Experience}

\subsection*{TheCAT}
\begin{itemize}

    \item Oct 2010 - Present
    \item Worked as a part of the Unix/Linux team administering servers, services, and networking
    \item Gained experience with and exposure to: IOS, NX-OS, ipv6, Puppet, Puppet module development, NFS, Autofs, Samba, iSCSI, KVM, libvirt, Xen, Ganeti, LVM, ZFS, DHCP, PXE/Syslinux, DNS, SunRay Thinclients/Server, LDAP: OpenDS, OpenLDAP, sunONE Directory server, Apache, Linux, FreeBSD, Solaris, Out-of-band management interfaces, VNC, Tomcat, Amanda Network Backup, serial based managment, Zenoss, OpenNMS, IRC server administration, git on the server: gitosis and gitolite, exotic *nixes: The Hurd, Nextenta, OpenSolaris
    \item Developed team-based skills and experience: IRC, git, tickets, self-documenting on wiki, procmail
    \item Worked the front desk dealing with users in person and on the phone.
    \item Cultivated important meta skills: how to work on something completely new to me, how to maintain a service that was setup by someone who has left the institution, how to build utility scripts as I go

    \item \textbf{Relevant Because:} The CAT gave me first hand experience with manual and automated system administration, and front line user interaction.
 
\end{itemize}

\subsection*{Lab Experience}
\begin{itemize}

    \item Aug 2010 - Aug 2011
    \item Worked as a student researcher in a Physics lab doing carbon nanotube simulations.
    \item Sole programmer, working in python, developing a nanotube creation algorithm worthy of publication.
    \item Learned how to ask my friends, colleagues, even strangers for help and advice, especially when debugging and choosing algorithms. No one need debug alone.
    \item \textbf{Relevant Because:} Worked alone on long term coding project in a dynamic programing language.

\end{itemize}


\bigskip

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}

\end{document}
