% William Van Hevelingen - Curriculum Vitae
% 
%
% Copyright (C) 2012 William Van Hevelingen
% Copyright (C) 2012 Spencer Krum
% 
% Template (C) 2004-2010 - Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Fonts
\usepackage[T1]{fontenc}
% \usepackage[bitstream-charter]{mathdesign}
% \usepackage[scaled=0.85]{beramono}

% Set your name here
\def\name{William Van Hevelingen}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {resume},
  pdftitle = {\name: William Van Hevelingen Resume},
  pdfsubject = {William Van Hevelingen},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  William Van Hevelingen\\
  3121 NE Chehalem Dr.\\
  Newberg, OR 97132
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Mobile: (971) 832-9862 \\
  Email: \texttt{wvan@cs.pdx.edu} \\
  Homepage: \texttt{http://github.com/blkperl} \\
\end{minipage}

% \section*{Objective}

%\\
\section*{Experience}

\subsection*{Lead Unix System Administrator (Portland State University / TheCAT)}

\begin{itemize}
    \item Aug 2012 - Present
    \item Oversaw all Unix and Linux servers and desktops for the College of Engineering and managed a team of student workers and volunteers.
    \item Supervised and assisted in implementing migration from legacy Sun Directory servers to OpenLDAP.
    \item Built RHEL/Centos environment and migrated Solaris CAD tools to RHEL5.
    \item Built Solaris 11 environment and migrated Solaris 10 fileservers to new platform.
    \item Implemented Redmine 1.x to Redmine 2.x migration and built a self-service portal for project and repository creation.
    \item Setup Nagios and Graphite for improved monitoring and metrics.
\end{itemize}

\subsection*{Unix System Administrator - Student Worker (Portland State University / TheCAT)}
\begin{itemize}

    \item Oct 2009 - Aug 2012
    \item Deployed and maintained Unix/Linux services.
    \item Wrote and integrated Puppet modules for our environment.
    \item Worked on the Networking team activating switch ports and debugging network problems.
    \item Trained and taught new volunteers Unix as part of theCAT's braindump program.


\end{itemize}

\subsection*{MECOP Software Developer Internship (ON Semiconductor)}
\begin{itemize}

    \item April 2011 - Sep 2011
    \item Worked as C\# webapp developer on internal Business applications
    \item Designed and implemented web apps, console applications, and class libraries within the .NET framework.
    \item Wrote SQL queries to generate reports for the Business Team to analyze trends and patterns in the production line.
    \item Migrated all legacy applications with local users or legacy ldap server to use AD authentication.
    \item Migrated business applications, perl scripts, user configuration on a Solaris 9 server to a RHEL6 server.

\end{itemize}

\begin{minipage}[t]{0.5\textwidth}
\section*{Education}
\begin{itemize}

  \item B.S., Computer Science
  \item Portland State University, Portland, OR
  \item Expected graduation: Fall 2014
  
\end{itemize}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\section*{Other}
\begin{itemize}
\item Co-Author of Pro Puppet Edition II
\item Community Puppet Module Maintainer
\end{itemize}
\end{minipage}

\renewenvironment{itemize}{
  \begin{list}{$\bullet$}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}


\bigskip

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}

\end{document}
